APPM report - Draft

### 2022-09-30 paper_version/main.tex
Polish the first part: plasma model

\section{Introduction}
Under moderate assumptions, plasmas, which are mixed gases of charged particles, can be treated as fluid and described by hydrodynamic equations. The Maxwell equations are involved to describe their induction of and interaction with electromagnetic fields. In this work, we discuss and implement this so-called \emph{Euler-Maxwell} system with a focus on its limiting behavior of quasi-neutrality, namely when the \emph{Debye length} goes to zero. The dimensionless form of the Euler-Maxwell equations is parameterized by the rescaled Debye length $\lambda$ whose vanishing limit alters the mathematical nature of the equations. To be more concrete, the non-limit model ($\lambda = \mathcal{O}(1)$) is hyperbolic where information spreads with a finite speed whereas the limit model ($\lambda \rightarrow 0$) becomes elliptic, and any changes immediately influence the whole domain. In other words, the perturbation of $\lambda$ in the Maxwell-Euler system poses a singular perturbation problem. Such switching makes it difficult to handle both models in a single implementation framework, which, however, is desired in many cases where both models coexist in the computational domain. Now comes the concept of \emph{asymptotic-preserving}(AP) scheme. We turn to the celebrated commuting diagram Fig. \ref{fig:commuting_diagram_ap} for illustration.\todo{add illustration of AP schemes}.

@@

\begin{figure}
    \centering
    \begin{tikzpicture}
    \node (nw) {\Large $P^\lambda_h$};
    \node (ne) [right=3cm of nw]{\Large $P^\lambda$};
    \node (sw) [below=of nw]{\Large $P^0_h$};
    \node (se) [right=3cm of sw]{\Large $P^0$};
    \draw[->] (nw.east)  -- node [above,midway] {$h\rightarrow0$} (ne.west) ;
    \draw[->] (nw.east)  --  (ne.west) ;
    \draw[->] (nw.south) -- node [left,midway] {$\lambda\rightarrow0$} (sw.north);
    \draw[->] (nw.south) -- node {} (sw.north);
    \draw[->] (sw.east)  -- node [above,midway] {$h\rightarrow0$}(se.west);
    \draw[->] (ne.south) -- node [left,midway] {$\lambda\rightarrow0$} (se.north);
    \end{tikzpicture}
    \caption{Commuting diagram of AP schemes}
    \label{fig:commuting_diagram_ap}
\end{figure}

\section{The Maxwell-Euler System and its Rescalling}
\subsection{Full plasma fluid model}
The Maxwell system is described by Maxwell's equations whose expression in SI units read
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday} \\ 
    \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= -\mathbf{J}, \label{equ:maxwell_ampere} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B}\\
    \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D}
\end{align}
where the involved quantities are magnetic flux density $\mathbf{B}$, electric field intensity $\mathbf{E}$, electric induction $\mathbf{D}$, magnetic field intensity $\mathbf{H}$, electric current density $\mathbf{J}$ and electric charge density $\rho$. These equations are known as Faraday's law (\ref{equ:maxwell_faraday}), Amp\`{e}re's law (\ref{equ:maxwell_ampere}), Gauss's law for magnetism (\ref{equ:maxwell_gauss_B}) and Gauss's law for electric field (\ref{equ:maxwell_gauss_D}). For simplicity, we only consider isotropic and homogeneous mediums in vacuum. The quantities are thus related by the linear constitutive relations 
\begin{equation*}
    \mathbf{D} = \varepsilon_0 \mathbf{E}, \ \ \ \mathbf{B} = \mu_0\mathbf{H}, 
\end{equation*}
where $\varepsilon_0$ and $\mu_0$ are the vacuum permittivity and permeability of the medium. By definition of the electric current density $\mathbf{J}$ and electric charge density $\rho$, they are supposed to satisfy the continuity equation
\begin{equation} \label{equ:charge_continuity}
    \partial_t\rho + \nabla \cdot \mathbf{J} = 0.
\end{equation}
Besides, on taking the divergence of equations (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) together with the relation (\ref{equ:charge_continuity}), it is possible to verify that Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are consequences of (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) provided that (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are satisfied at the initial time. In other words, Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are redundant, and Faraday's law (\ref{equ:maxwell_faraday}) and Amp\`{e}re's law (\ref{equ:maxwell_ampere}) suffice.

In the Euler system, the motions of gas particles are accounted for through the \emph{Euler equations}. Specifically, we equip each species with one set of (compressible) Euler equations, taking into account the effect of electromagnetic fields as well as other processes like collisions and recombination. The generic expressions read
\begin{align} \label{equ:euler_}
    \partial_t
    \begin{bmatrix}
    n_* \\
    m_*n_* \mathbf{u}_* \\
    m_*n_* e_*
    \end{bmatrix}
    + \nabla \cdot
    \begin{bmatrix}
    n_* \mathbf{u}_* \\
    m_*n_* \mathbf{u}_* \otimes \mathbf{u}_* + p_*\mathbb{I} \\
    m_*n_* h_* \mathbf{u}_*
    \end{bmatrix}
    =
    \begin{bmatrix}
    0 \\
    q_*n_*(\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
    \mathbf{J}_* \cdot \mathbf{E}
    \end{bmatrix}
    +
    \begin{bmatrix}
    \Gamma_* \\
    \mathbf{R}_* \\
    Q_*
    \end{bmatrix}.
\end{align}
The subscript $*$ represents the indices for different species, and by convention we assign $* = e$ to electrons, $* = i$ to ions, and $* = n$ to neutral atoms. The involved fluid quantities are: number density $n_*$, particle mass $m_*$,  charge number $q_*$, velocity $\mathbf{u}_*$, pressure $p_*$, specific total energy $e_* := \frac{1}{2}|\mathbf{u}_*|^2 + \frac{p_*}{m_*n_*(\gamma - 1)}$, specific total enthalpy $h_* := e_* + \frac{p_*}{m_*n_*}$ and current density $\mathbf{J}_* := q_*n_*\mathbf{u}_*$. All the species are assumed ideal gases with heat capacity ratio $\gamma=5/3$ for monatomic gases. The left-hand side of the equations describes the convection of plasma fluids. The first term at the right-hand side denotes Lorentz force in the momentum equation and Joule heating in the energy equation. $\Gamma_*, \mathbf{R}_*, Q_*$ are generic terms that include effects of inter-species collision, ionization, recombination, etc.

For the sake of simplicity, we would only consider ion-electron collision in this work. Such collisions are modeled by friction terms as follows, and we simply present the expressions without derivation (see \citep[][sec. 5.6.2]{chen2016}):
\begin{equation} \label{equ:collision}
    \mathbf{R}_{e}^{\text{coll}} = \frac{\pi Ze^4m_e^{1/2}}{(4\pi\varepsilon_0)^2(k_BT_e)^{3/2}}\text{ln}\Lambda n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_{i}^{\text{coll}},  
\end{equation}
which models the collision force that is applied on the electrons. ln$\Lambda$ is called the \emph{Coulomb logarithm}, which typically takes a numerical value of order 10–20 . Because of the conservation of momentum, the collision term experienced by ions $\mathbf{R}_{i}^{\text{coll}}$ is just the negative of $\mathbf{R}_{e}^{\text{coll}}$. For full details about the ionization and recombination, readers are referred to \cite{fuchs_2021}.

@@

\subsection{Rescaled Maxwell-Euler system}
The multi-scale nature of the Euler-Maxwell system is revealed by defining different dimensionless parameters. In particular, the quasi-neutrality approximation is clarified. The rescaling procedure mostly sticks to that of \cite{degond_2017}.

First, typical values for each quantity, as well as the characteristic length and time scale are specified. Rescaled by these values, the magnitude of each term of the equations can be compared according to the presumption on the magnitude of these typical values. We define $\overline{x}$ and $\overline{t}$ as space and time scale of interest, by which the reference velocity $\overline{v}$ is defined as $\overline{x}/\overline{t}$. The typical magnitudes of electromagnetic fields are $\overline{E}$ and $\overline{B}$. The typical magnitudes of fluid quantities are denoted by $\overline{u}$ for plasma drift velocity, $\overline{n}$ for plasma number density, $\overline{T}$ for plasma temperature. On top of that, the typical pressure is set $\overline{n}k_B\overline{T}$ with $k_B$ being the Boltzmann constant; the typical value for the specific total energy and enthalpy is set $\overline{u}^2$. Together with the physical parameters, namely, permittivity $\varepsilon_0$, permeability $\mu_0$, light speed $c^2 = (\varepsilon_0\mu_0)^{-1}$, Boltzmann constant $k_B$, the elementary charge $e$, and ion mass $m_i$, the following dimensionless parameters are induced,
\begin{align*} 
    \xi &:= \frac{\overline{v}}{c} \text{ the velocity of interest to the light speed}, &\\
    \zeta &:= \frac{\overline{u}}{\overline{v}} \text{ the plasma velocity to the speed of interest}, &\\
    M &:= \frac{\overline{u}}{v_{th,i}} \text{ the plasma drift velocity to the thermal speed of ions, where } v_{th,i} := \left(\frac{k_B \overline{T}}{m_i}\right)^{1/2}, &\\
    \eta &:= \frac{e\overline{E}\overline{x}}{m_i\overline{u}^2} \text{ the electric energy to the kinetic energy of ions}, &\\
    \beta &:= \frac{\overline{v}\overline{B}}{\overline{E}} \text{ the induced electric field to the total electric field}, &\\
    \lambda &:= \frac{\lambda_D}{\overline{x}} \text{ the dimensionless Debye length, where }\lambda_D := \left(\frac{\varepsilon_0k_B\overline{T}}{e^2\overline{n}}\right)^{1/2}, &\\
    \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass ratio to the ion mass},\ \  * \in \{i,e,n,\cdots\}, &\\
    g &:= \frac{1}{\overline{n}\lambda_D^3} \text{ the plasma parameter\footnotemark}.&
\end{align*}
\footnotetext{It is basically the reciprocal of the number of particles per Debye sphere, see \cite[][sec. 1.1]{gibbon2020}. Classical plasma theory assumes $g \ll 1$.}

The Euler-Maxwell system (\ref{equ:maxwell_faraday}) to (\ref{equ:euler_}) is readily to be rescaled by nondimensionalizing each quantity with respect to its typical value. By abuse of notation, the dimensionless quantities have the same symbol with their original ones without incurring any ambiguity. For simplicity, we only consider the collision terms, namely $\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = 0$ in (\ref{equ:euler_}), while neglecting other effects. The rescaled Euler-Maxwell system reads
\begin{align}
    \beta \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescalling} \\ 
    \lambda^2 \partial_t \mathbf{E} - \frac{\beta \lambda^2}{\xi^2}\nabla \times \mathbf{B} &= - \frac{\zeta}{\eta M^2}\mathbf{J}, \label{equ:maxwell_ampere_rescalling} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescalling}\\
    \lambda^2 \eta M^2 \nabla \cdot \mathbf{E} &= \rho, \label{equ:maxwell_gauss_D_rescalling} \\
    \partial_t
    \begin{bmatrix}
    n_* \\
    n_* \mathbf{u}_* \\
    n_* e_*
    \end{bmatrix}
    + \nabla \cdot
    \begin{bmatrix}
    \zeta n_* \mathbf{u}_* \\
    \zeta n_* \mathbf{u}_* \otimes \mathbf{u}_* + \zeta M^{-2} \varepsilon_*^{-2} p_*\mathbb{I} \\
    \zeta n_* h_* \mathbf{u}_*
    \end{bmatrix}
    &=
    \begin{bmatrix}
    0 \\
    \eta \zea \varepsilon_*^{-2} q_* n_*\mathbf{E} + \eta \zeta^2 \beta \varepsilon_*^{-2} q_* n_* \mathbf{u}_* \times \mathbf{B} \\
    \zeta \eta \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
    \end{bmatrix} +
    \begin{bmatrix}
    0 \\
    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
    0 
    \end{bmatrix}, \label{equ:euler_rescalling}
\end{align}
where the equation of state becomes $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + M^{-2}\frac{p_*}{\epsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + M^{-2}\frac{p_*}{\epsilon^2_* n_*}$. For a fully-ionized gas, we have the original expression of $\mathbf{R}_*^{\text{coll}}$ in (\ref{equ:collision}), and its rescaled expression becomes
\begin{equation*}
    \mathbf{R}_i^{\text{coll}} = \frac{Z\text{ln}\Lambda}{16\pi}g\lambda^{-1}M^{-1}\varepsilon_en_en_i(\mathbf{u}_i - \mathbf{u}_e). 
\end{equation*}

@@

Under such assumptions on these dimensionless parameters, the rescaled Euler-Maxwell system is simplified into a parametrized system with the dimensionless Debye length $\lambda$ being the asymptotic parameter
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescaled} \\ 
    \lambda^2 \partial_t \mathbf{E} - \nabla \times \mathbf{B} &= - \mathbf{J}, \label{equ:maxwell_ampere_rescaled} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescaled}\\
    \lambda^2 \nabla \cdot \mathbf{E} &= \rho, \label{equ:maxwell_gauss_D_rescaled} \\
    \partial_t
    \begin{bmatrix}
    n_* \\
    n_* \mathbf{u}_* \\
    n_* e_*
    \end{bmatrix}
    + \nabla \cdot
    \begin{bmatrix}
    n_* \mathbf{u}_* \\
    n_* \mathbf{u}_* \otimes \mathbf{u}_* + \varepsilon_*^{-2} p_*\mathbb{I} \\
    n_* h_* \mathbf{u}_*
    \end{bmatrix}
    &=
    \begin{bmatrix}
    0 \\
    \varepsilon_*^{-2} q_* n_* (\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
    \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
    \end{bmatrix}+
    \begin{bmatrix}
    0 \\
    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
    0 
    \end{bmatrix}, \label{equ:euler_rescaled}
\end{align}
with the equation of state $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + \frac{p_*}{\varepsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + \frac{p_*}{\varepsilon^2_* n_*}$. For a fully-ionized gas with only ions and electrons, 
\begin{equation} \label{equ:collision_rescaled} 
    \mathbf{R}_i^{\text{coll}} = \alpha^{\text{coll}}n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_e^{\text{coll}}.
\end{equation}

Although the rescaling of the equations involves considerable physical intuitions on the decision of typical values and their magnitudes, which is crucial to reach a physically meaningful problem, we are now in a position to forget this reasoning, and focus on the singular perturbation problem parameterized by $\lambda$. The rescaling enables us to identify the magnitude of each term of the equations, which is revealed by the prefactor polynomial of $\lambda$.

\subsection{Quasi-neutral limit} \label{sec:quasi-neutral_limit}
As is already discussed in section \ref{sec:quasi-neutrality}, the quasi-neutrality, being an important character of plasmas, refers to the fact that the net charge of the free electrons and ions in plasmas cancel out over an area of the same order as the Deybe length $\lambda_D$. When the typical length scale $\overline{x}$ is of magnitudes larger than $\lambda_D$, the condition $\rho = 0$ can be approximately satisfied.

>>>>

\section{Plasma model}
Under moderate assumptions, plasmas, which are gases composed of charged particles (and possibly neutral particles), can be treated as fluid and described by hydrodynamic equations. The Maxwell equations are involved to describe their induction of and interaction with electromagnetic fields.

\todo{A bit more on the physical background}.

After rescalling all the variables with respect to the prescribed reference units, the Debye length $\lambda_D$, characterizing the charge screening ability of the plasma, would pop up and its zero limit, which is what we called \emph{quasineutral limit}, is of great interest, since the limit model largely simplifies the system and in many cases the accuracy of the assumption is satisfactory enough.

In this section, the multi-species Maxwell-Euler equations with collision term is introduced first, followed by detailed rescalling procedure. The quasi-neutral model will be make clear by letting the rescalled Debye length $\lambda$ go to zero. Afterwards, a set of boundary conditions are presented and its validity to both non-limit and limit model is discussed. Finally, we would like to present a reformulation of the system which would be crucial to the stability of the numerical scheme.

\begin{comment}
In this work, we discuss and implement the so-called \emph{Euler-Maxwell} system with a focus on its limiting behavior of quasi-neutrality, namely when the \emph{Debye length} goes to zero. The dimensionless form of the Euler-Maxwell equations is parameterized by the rescaled Debye length $\lambda$ whose vanishing limit alters the mathematical nature of the equations. To be more concrete, the non-limit model ($\lambda = \mathcal{O}(1)$) is hyperbolic where information spreads with a finite speed whereas the limit model ($\lambda \rightarrow 0$) becomes elliptic, and any changes immediately influence the whole domain. In other words, the perturbation of $\lambda$ in the Maxwell-Euler system poses a singular perturbation problem. Such switching makes it difficult to handle both models in a single implementation framework, which, however, is desired in many cases where both models coexist in the computational domain. Now comes the concept of \emph{asymptotic-preserving}(AP) scheme. We turn to the celebrated commuting diagram Fig. \ref{fig:commuting_diagram_ap} for illustration.\todo{add illustration of AP schemes}.

@@

\begin{figure}
    \centering
    \begin{tikzpicture}
    \node (nw) {\Large $P^\lambda_h$};
    \node (ne) [right=3cm of nw]{\Large $P^\lambda$};
    \node (sw) [below=of nw]{\Large $P^0_h$};
    \node (se) [right=3cm of sw]{\Large $P^0$};
    \draw[->] (nw.east)  -- node [above,midway] {$h\rightarrow0$} (ne.west) ;
    \draw[->] (nw.east)  --  (ne.west) ;
    \draw[->] (nw.south) -- node [left,midway] {$\lambda\rightarrow0$} (sw.north);
    \draw[->] (nw.south) -- node {} (sw.north);
    \draw[->] (sw.east)  -- node [above,midway] {$h\rightarrow0$}(se.west);
    \draw[->] (ne.south) -- node [left,midway] {$\lambda\rightarrow0$} (se.north);
    \end{tikzpicture}
    \caption{Commuting diagram of AP schemes}
    \label{fig:commuting_diagram_ap}
\end{figure}
\end{comment}

\subsection{The Maxwell-Euler System}
The Maxwell system is described by Maxwell's equations whose expression in SI units read
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday} \\ 
    \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= -\mathbf{J}, \label{equ:maxwell_ampere} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B}\\
    \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D}
\end{align}
where the involved quantities are magnetic flux density $\mathbf{B}$, electric field intensity $\mathbf{E}$, electric induction $\mathbf{D}$, magnetic field intensity $\mathbf{H}$, electric current density $\mathbf{J}$ and electric charge density $\rho$. These equations are known as Faraday's law (\ref{equ:maxwell_faraday}), Amp\`{e}re's law (\ref{equ:maxwell_ampere}), Gauss's law for magnetism (\ref{equ:maxwell_gauss_B}) and Gauss's law for electric field (\ref{equ:maxwell_gauss_D}). For simplicity, we only consider isotropic and homogeneous mediums in vacuum. We consider the linear constitutive relations 
\begin{equation*}
    \mathbf{D} = \varepsilon_0 \mathbf{E}, \ \ \ \mathbf{B} = \mu_0\mathbf{H}, 
\end{equation*}
where $\varepsilon_0$ and $\mu_0$ are the vacuum permittivity and permeability of the medium. By definition of the electric current density $\mathbf{J}$ and electric charge density $\rho$, they are supposed to satisfy the continuity equation
\begin{equation} \label{equ:charge_continuity}
    \partial_t\rho + \nabla \cdot \mathbf{J} = 0.
\end{equation}
Besides, on taking the divergence of equations (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) together with the relation (\ref{equ:charge_continuity}), it is possible to verify that Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are consequences of (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) provided that (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are satisfied at the initial time. In other words, Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) serve as initial conditions. Faraday's law (\ref{equ:maxwell_faraday}) and Amp\`{e}re's law (\ref{equ:maxwell_ampere}) suffice.

In the Euler system, the motions of gas particles are accounted for through the \emph{Euler equations}. Specifically, we equip each species with one set of (compressible) Euler equations, taking into account the effect of electromagnetic fields as well as other processes like collisions and recombination. The generic expressions read
\begin{align} \label{equ:euler_}
    \partial_t
    \begin{bmatrix}
    n_* \\
    m_*n_* \mathbf{u}_* \\
    m_*n_* e_*
    \end{bmatrix}
    + \nabla \cdot
    \begin{bmatrix}
    n_* \mathbf{u}_* \\
    m_*n_* \mathbf{u}_* \otimes \mathbf{u}_* + p_*\mathbb{I} \\
    m_*n_* h_* \mathbf{u}_*
    \end{bmatrix}
    =
    \begin{bmatrix}
    0 \\
    q_*n_*(\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
    \mathbf{J}_* \cdot \mathbf{E}
    \end{bmatrix}
    +
    \begin{bmatrix}
    \Gamma_* \\
    \mathbf{R}_* \\
    Q_*
    \end{bmatrix}.
\end{align}
The subscript $*$ represents the indices for different species, and by convention we assign $* = e$ to electrons, $* = i$ to ions, and $* = n$ to neutral atoms. The involved fluid quantities are: number density $n_*$, particle mass $m_*$,  charge number $q_*$, velocity $\mathbf{u}_*$, pressure $p_*$, specific total energy $e_* := \frac{1}{2}|\mathbf{u}_*|^2 + \frac{p_*}{m_*n_*(\gamma - 1)}$, specific total enthalpy $h_* := e_* + \frac{p_*}{m_*n_*}$ and current density $\mathbf{J}_* := q_*n_*\mathbf{u}_*$. All the species are assumed ideal gases with heat capacity ratio $\gamma=5/3$ for monatomic gases. The left-hand side of the equations describes the convection of plasma fluids. Note that the heat conduction is omitted in the energy equation. The first term at the right-hand side denotes Lorentz force in the momentum equation and Joule heating in the energy equation. $\Gamma_*, \mathbf{R}_*, Q_*$ are generic terms that include effects of inter-species collision, ionization, recombination, etc.

For the sake of simplicity, we would only consider ion-electron collision in this work. Under moderate assumptions, such collisions can be well modelled by friction terms, and we simply present the expressions without derivation (see \citep[][sec. 5.6.2]{chen2016}):
\begin{equation} \label{equ:collision}
    \mathbf{R}_{e}^{\text{coll}} = \frac{\pi Ze^4m_e^{1/2}}{(4\pi\varepsilon_0)^2(k_BT_e)^{3/2}}\text{ln}\Lambda n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_{i}^{\text{coll}},  
\end{equation}
which models the collision force that is applied on the electrons. ln$\Lambda$ is called the \emph{Coulomb logarithm}, which typically takes a numerical value of order 10–20 . Because of the conservation of momentum, the collision term experienced by ions $\mathbf{R}_{i}^{\text{coll}}$ is nothing but the negation of $\mathbf{R}_{e}^{\text{coll}}$. For full details about the ionization and recombination, readers are referred to \cite{fuchs_2021}.

@@

\subsection{Rescalling}
In the rescalling, the variables in the equations are taken as the ratio of their original quantities and reference units, which transforms the system into a dimensionless form. The magnitudes of the dimensionless numbers are indications of the magnitude of corresponding terms. In this part, the rescalling procedure mostly sticks to that of \cite{degond_2017}.

First, reference units for each quantity, e.g. the characteristic length and time scale, are prescribed. We define $\overline{x}$ and $\overline{t}$ as space and time scale of interest, by which the reference velocity $\overline{v}$ is defined as $\overline{x}/\overline{t}$. The typical magnitudes of electromagnetic fields are $\overline{E}$ and $\overline{B}$. The typical magnitudes of fluid quantities are denoted by $\overline{u}$ for plasma drift velocity, $\overline{n}$ for plasma number density, $\overline{T}$ for plasma temperature. On top of that, the typical pressure is set $\overline{n}k_B\overline{T}$ with $k_B$ being the Boltzmann constant; the typical value for the specific total energy and enthalpy is set $\overline{u}^2$. Together with the physical parameters, namely, permittivity $\varepsilon_0$, permeability $\mu_0$, light speed $c^2 = (\varepsilon_0\mu_0)^{-1}$, Boltzmann constant $k_B$, the elementary charge $e$, and ion mass $m_i$, the following dimensionless parameters are induced,
\begin{align*} 
    \xi &:= \frac{\overline{v}}{c} \text{ the velocity of interest to the light speed}, &\\
    \zeta &:= \frac{\overline{u}}{\overline{v}} \text{ the plasma velocity to the speed of interest}, &\\
    M &:= \frac{\overline{u}}{v_{th,i}} \text{ the plasma drift velocity to the thermal speed of ions, where } v_{th,i} := \left(\frac{k_B \overline{T}}{m_i}\right)^{1/2}, &\\
    \eta &:= \frac{e\overline{E}\overline{x}}{m_i\overline{u}^2} \text{ the electric energy to the kinetic energy of ions}, &\\
    \beta &:= \frac{\overline{v}\overline{B}}{\overline{E}} \text{ the induced electric field to the total electric field}, &\\
    \lambda &:= \frac{\lambda_D}{\overline{x}} \text{ the dimensionless Debye length, where }\lambda_D := \left(\frac{\varepsilon_0k_B\overline{T}}{e^2\overline{n}}\right)^{1/2}, &\\
    \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass ratio to the ion mass},\ \  * \in \{i,e,n,\cdots\}, &\\
    g &:= \frac{1}{\overline{n}\lambda_D^3} \text{ the plasma parameter\footnotemark}.&
\end{align*}
\footnotetext{It is basically the reciprocal of the number of particles per Debye sphere, see \cite[][sec. 1.1]{gibbon2020}. Classical plasma theory assumes $g \ll 1$.}

By abuse of notation, the dimensionless quantities have the same symbol with their original ones without incurring any ambiguity. For the sake of simplicity, we only consider the collision terms, namely $\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = Q_*^\text{coll}$ in (\ref{equ:euler_}), while neglecting other effects. The rescaled Euler-Maxwell system reads
\begin{align}
    \beta \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescalling} \\ 
    \lambda^2 \partial_t \mathbf{E} - \frac{\beta \lambda^2}{\xi^2}\nabla \times \mathbf{B} &= - \frac{\zeta}{\eta M^2}\mathbf{J}, \label{equ:maxwell_ampere_rescalling} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescalling}\\
    \lambda^2 \eta M^2 \nabla \cdot \mathbf{E} &= \rho, \label{equ:maxwell_gauss_D_rescalling} \\
    \partial_t
    \begin{bmatrix}
    n_* \\
    n_* \mathbf{u}_* \\
    n_* e_*
    \end{bmatrix}
    + \nabla \cdot
    \begin{bmatrix}
    \zeta n_* \mathbf{u}_* \\
    \zeta n_* \mathbf{u}_* \otimes \mathbf{u}_* + \zeta M^{-2} \varepsilon_*^{-2} p_*\mathbb{I} \\
    \zeta n_* h_* \mathbf{u}_*
    \end{bmatrix}
    &=
    \begin{bmatrix}
    0 \\
    \eta \zea \varepsilon_*^{-2} q_* n_*\mathbf{E} + \eta \zeta^2 \beta \varepsilon_*^{-2} q_* n_* \mathbf{u}_* \times \mathbf{B} \\
    \zeta \eta \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
    \end{bmatrix} +
    \begin{bmatrix}
    0 \\
    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
    \varepsilon_*^{-2}Q_*^{\text{coll}} 
    \end{bmatrix}, \label{equ:euler_rescalling}
\end{align}
where the equation of state becomes $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + M^{-2}\frac{p_*}{\epsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + M^{-2}\frac{p_*}{\epsilon^2_* n_*}$. For a fully-ionized gas, we have the original expression of $\mathbf{R}_*^{\text{coll}}$ in (\ref{equ:collision}), and its rescaled expression becomes
\begin{equation*}
    \mathbf{R}_i^{\text{coll}} = \frac{Z\text{ln}\Lambda}{16\pi}g\lambda^{-1}M^{-1}\varepsilon_en_en_i(\mathbf{u}_i - \mathbf{u}_e). 
\end{equation*}

@@

Under such assumptions on these dimensionless parameters, the rescaled Euler-Maxwell system is simplified into a parametrized system with the dimensionless Debye length $\lambda$ being the asymptotic parameter
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescaled} \\ 
    \lambda^2 \partial_t \mathbf{E} - \nabla \times \mathbf{B} &= - \mathbf{J}, \label{equ:maxwell_ampere_rescaled} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescaled}\\
    \lambda^2 \nabla \cdot \mathbf{E} &= \rho, \label{equ:maxwell_gauss_D_rescaled} \\
    \partial_t
    \begin{bmatrix}
    n_* \\
    n_* \mathbf{u}_* \\
    n_* e_*
    \end{bmatrix}
    + \nabla \cdot
    \begin{bmatrix}
    n_* \mathbf{u}_* \\
    n_* \mathbf{u}_* \otimes \mathbf{u}_* + \varepsilon_*^{-2} p_*\mathbb{I} \\
    n_* h_* \mathbf{u}_*
    \end{bmatrix}
    &=
    \begin{bmatrix}
    0 \\
    \varepsilon_*^{-2} q_* n_* (\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
    \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
    \end{bmatrix}+
    \begin{bmatrix}
    0 \\
    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
    \varepsilon_*^{-2}Q_*^{\text{coll}} 
    \end{bmatrix}, \label{equ:euler_rescaled}
\end{align}
with the equation of state $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + \frac{p_*}{\varepsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + \frac{p_*}{\varepsilon^2_* n_*}$. For a fully-ionized gas with only ions and electrons, 
\begin{equation} \label{equ:collision_rescaled} 
    \mathbf{R}_i^{\text{coll}} = \alpha^{\text{coll}}n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_e^{\text{coll}},
\end{equation}
and consequently, the rescaled friction heat for ions and electrons takes the expression
\begin{align*} 
    Q_i^{\text{coll}} &= \alpha^{\text{coll}}n_en_i \mathbf{u}_i (\mathbf{u}_i - \mathbf{u}_e), \\
    Q_e^{\text{coll}} &= \alpha^{\text{coll}}n_en_i \mathbf{u}_e (\mathbf{u}_e - \mathbf{u}_i).
\end{align*}

We end up getting the rescaled Maxwell-Euler system parameterized by $\lambda$. The rescaling enables us to identify the magnitude of each term in the equations, which is revealed by the prefactor polynomial of $\lambda$.
